A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-05-11 ICLP Paper/samplepaper.tex
extended abstract and introduction in view of 2nd round comments by Reviewer 3

%\usepackage{comment}
%\usepackage{algorithm} 
%\usepackage{algpseudocode}
\usepackage{soul}%{color,soul}

@@

In this paper, we propose problem decomposition into time windows whose operations can be successively scheduled and optimized by means of multi-shot ASP solving.

@@

@@

The contributions of our work going beyond the study in \citep{elkgeb20a} are:
\begin{itemize}
\item In addition to problem decomposition based on the earliest starting times
      of operations, we consider the most total work remaining criterion and
      refinements of both strategies by bottleneck machines.
      We encode static as well as dynamic decomposition variants, the latter taking
      partial schedules for operations of previous time windows into account, by stratified
      ASP programs (without DL constraints).
\item Since a decomposition into time windows may be incompatible with
      the optimal sequences of operations sharing a machine, we incorporate
      overlapping time windows into the iterative scheduling process to
      offer a chance for revising ``decomposition mistakes''.
      Moreover, the makespan objective, which we apply to optimize (partial) schedules, tolerates unnecessary idle times of machines as long as they do not yield a greater scheduling horizon. 
      Therefore, we devise a stratified ASP encoding to postprocess and compress partial schedules by reassigning operations to earlier idle slots available on their machines.
\item We experimentally evaluate decomposition strategies varying the number of
      operations per time window, as well as multi-shot ASP, solving
      augmented with overlapping and compression techniques
      on JSP benchmark sets of several sizes.
      In particular, our experiments demonstrate that successive optimization
      by multi-shot ASP solving leads to substantially better schedules within
      tight runtime limits than global optimization on the full problem,
      where the gap increases with the number of operations to schedule.
\end{itemize}

@@

we also ran the state-of-the-art CP system OR-tools (version 9.2)} \citep{ortools}\hl{

>>>>

%\usepackage{comment}
%\usepackage{algorithm} 
%\usepackage{algpseudocode}
\usepackage{soul}%{color,soul}
\usepackage{pagecolor}
\sethlcolor{\thepagecolor}

@@

In this paper, we propose problem decomposition into time windows whose operations can be successively scheduled and optimized by means of multi-shot Answer Set Programming (ASP) solving.

@@

While the obtained solution quality still remains behind a state-of-the-art Constraint
Programming system, our multi-shot solving approach comes closer the larger the instance
size, demonstrating good scalability by problem decomposition.

@@

The contributions of our work going beyond the study in \citep{elkgeb20a} are:
\begin{itemize}
\item In addition to problem decomposition based on the earliest starting times
      of operations, we consider the most total work remaining criterion and
      refinements of both strategies by bottleneck machines.
      We encode static as well as dynamic decomposition variants, the latter taking
      partial schedules for operations of previous time windows into account, by stratified
      ASP programs (without DL constraints).
\item Since a decomposition into time windows may be incompatible with
      the optimal sequences of operations sharing a machine, we incorporate
      overlapping time windows into the iterative scheduling process to
      offer a chance for revising ``decomposition mistakes''.
      Moreover, the makespan objective, which we apply to optimize (partial) schedules, tolerates unnecessary idle times of machines as long as they do not yield a greater scheduling horizon. 
      Therefore, we devise a stratified ASP encoding to postprocess and compress partial schedules by reassigning operations to earlier idle slots available on their machines.
\item We experimentally evaluate decomposition strategies varying the number of
      operations per time window, as well as multi-shot ASP, solving
      augmented with overlapping and compression techniques
      on JSP benchmark sets of several sizes.
      In particular, our experiments demonstrate that successive optimization
      by multi-shot ASP solving leads to substantially better schedules within
      tight runtime limits than global optimization on the full problem,
      where the gap increases with the number of operations to schedule.
      While the state-of-the-art CP system OR-tools \citep{ortools} is still ahead regarding the solution quality, our multi-shot solving approach % based on problem decomposition
      comes the closer the larger the instance size gets.
\end{itemize}

@@

we also ran the state-of-the-art CP system OR-tools (version 9.2)}\hl{
